
---
output: github_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# priceR 

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/priceR)](https://cran.r-project.org/package=priceR)
[![Travis build status](https://travis-ci.org/stevecondylios/priceR.svg?branch=master)](https://travis-ci.org/stevecondylios/priceR)
<!-- badges: end -->

`priceR` contains 4 types of capabilties:

- *Exchange Rates* - easily retrieve exchange rates for immediate use
- *Inflation* - easily inflate past (nominal) values into present day (real) prices
- *Regular Expressions* - easily extract common pricing patterns from free text
- *Formatting* - easily handle currencies in written work, including Rmarkdown documents 

`rawr` takes care of this.  

# Installation

Install from CRAN

```{r message=FALSE}
# install.packages("priceR")
library(priceR)
``` 

# Capabilties 

#### Exchange Rates

Retrieve exchange rate between a currency and 170 others:

```{r message=FALSE}

exchange_rate_latest("USD") 


# View full list of available currencies with currencies()
```


### Regular Expressions 

Extract numeric currencies from messy text data

```{r}

b[c(2,3,4,8,19,22,35,56,66,80,121), ] %>% extract_salary()




```








# Issues and Feature Requests

When reporting an issue, please include:

* Example code that reproduces the **observed** behavior.
* An explanation of what the **expected** behavior is.
* A specific url you're attempting to retrieve R code from (if that's what your issue concerns)


For feature requests, raise an issue with the following:

* The desired functionality
* Example inputs and desired output



# Pull Requests

Pull requests are welcomed. Before doing so, please create an issue or email me with your idea.  

Any new functions should follow the conventions established by the the package's existing functions. Please ensure

* Functions are sensibly named
* The __intent__ of the contribution is clear
* At least one example is provided in the documentation

















